\textbf{Are regime changes always bad economics? Evidence from daily financial data}

### 2023-07-03 doc/regime_changes_bp_rr.tex
Add charts of individual protest events

@@

>>>>

In addition, we independently plot the CARs during each period of protest preceding a resignation for each event.\footnote{An expception is the 1998 Yellow Revolution in the Philippines, as markets remained closed from the start of the protest until after Marcos' resignation}. This analysis also shows that volatility and the absolute value of returns increase during times of protest, but also reveals that the resignations themselves constitute distinct events that are clearly distinguishable from the general period of protest.

@@

\begin{figure}[!ht]
\includegraphics[scale=0.8]{../figs/bangla-1990.pdf}
\caption{CARs during the 1998 Indonesian revolution}
\label{fig:CAR-Egypt}
\end{figure}

\begin{figure}[!ht]
\includegraphics[scale=0.8]{../figs/indonesia-1998.pdf}
\caption{CARs during the 1998 Indonesian revolution}
\label{fig:CAR-Egypt}
\end{figure}

\begin{figure}[!ht]
\includegraphics[scale=0.8]{../figs/phil-2001.pdf}
\caption{CARs during the 1998 Indonesian revolution}
\label{fig:CAR-Egypt}
\end{figure}

\begin{figure}[!ht]
\includegraphics[scale=0.8]{../figs/argentina-2001.pdf}
\caption{CARs during the 2001 Argentinian riots}
\label{fig:CAR-Egypt}
\end{figure}

\begin{figure}[!ht]
\includegraphics[scale=0.8]{../figs/ukraine-2004.pdf}
\caption{CARs during the 2004 Orange Revolution}
\label{fig:CAR-Egypt}
\end{figure}

\begin{figure}[!ht]
\includegraphics[scale=0.8]{../figs/ecuador-2005.pdf}
\caption{CARs during the 2006 Nepalese Democracy Movement}
\label{fig:CAR-Egypt}
\end{figure}

\begin{figure}[!ht]
\includegraphics[scale=0.8]{../figs/nepal-2006.pdf}
\caption{CARs during the 2006 Nepalese Democracy Movement}
\label{fig:CAR-Egypt}
\end{figure}

\begin{figure}[!ht]
\includegraphics[scale=0.8]{../figs/tunisia-2011.pdf}
\caption{CARs during the 2011 Tunisian Revolution}
\label{fig:CAR-Egypt}
\end{figure}
